The Elements of Theses

### 2014-08-29 thesis/Acknowledgements.tex
re

\begin{acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

@@

Finally and most importantly, I would like to express my gratitude beyond 
words to my wife, Jiayin, who has been encouraging and inspiring me 
since we met in love. We went through all the difficlut times together,
and depended on each other in this foreign place one Pacific Ocean away from our homeland.
Every step forward I have made is unimaginable without Jiayin's support.

This dissertation study was supported in part by NSF IIS-1118106.
\end{acknowledgements}

>>>>

\begin{acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgments}

@@

Finally and most importantly, I would like to express my gratitude beyond 
words to my wife, Jiayin, who has been encouraging and inspiring me 
since we met in love. We went through all the difficult times together,
and depended on each other in this foreign place one Pacific Ocean away from our homeland.
Every step forward I have made is unimaginable without Jiayin's support.

This dissertation study was supported in part by NSF IIS-1118106.
Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and
do not necessarily reflect the views of Alibaba or the National Science Foundation.
\end{acknowledgements}
